Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-03-19 inst/surfing_jsa_rebuttal.tex

\textcolor{blue}{We have removed the inconsistency (and made the text
  more precise) by rephrasing the introduction which now reads:
  ``Competitive surfing involves surfers competing against one {\em or
    more} other surfers in heats\ldots''}

\subsection*{WSL not the main governing body}

Second statement is that the World Surf League is not the main
governing body of surfing competition. What about the International
Surfing Association, who organised and ran the Olympics, also run the
World Surfing games and national level competitions. The WSL really
only run professional level competition.

\textcolor{blue}{We have clarified that the WSL is the body for professional surfers}

@@

{\bf intent:}  Will put some statistical comment in here.

\subsection*{Brazilian preference}

Your hypothesis on Brazilians preference for reef breaking waves is based on what?

\textcolor{blue}{We have clarified the issue and corrected an
  unfortunate typographical error.  The manuscript reads: ``one
  suggestion (Burgess 2020, Ho 2021) is that Brazilian surfers tend to
  have skillsets that favour point and beach break wave types, readily
  accessible to these surfers' native Brazil; see (Scarfe 2003) for a
  scientific overview of surf break characteristics, and (Butt 2004)
  for a surfer's perspective''.  In short, we suggest that Brazilians
  {\em do not} like reef breaking waves.}

### 2022-03-19 inst/surfing_jsa.tex
refree: WSL is for professional surfers
referee: brazilians do not like reef breaking waves

Surfing is a popular and growing activity in terms of both
participation and viewing \citep{warshaw2010}.  Competitive surfing
involves surfers competing against one or multiple other surfers in heats
lasting 30-50 minutes \citep{booth1995}.  Points are awarded on a
10-point scale: each of five judges awards points to a surfer riding a
particular wave.  The World Surf League (WSL) is the main governing
body of surfing competitions \citep{wsl}.  The WSL conducts a world
tour in which the best ranked 34 surfers compete; in addition, at each
tour venue, two ``wildcard" surfers also enter the competition, who
are ignored here due to their generally poor performance and low
participation.

@@

\noindent where $p_H$ is a quantification of the beneficial home
ground effect.  Similar techniques have been used to account for the
first-move advantage in chess~\citep{hankin2020}, and here we apply it
to assess the supposed Brazilian preference for reef-breaking waves.

>>>>

Surfing is a popular and growing activity in terms of both
participation and viewing \citep{warshaw2010}.  Competitive surfing
involves surfers competing against one or multiple other surfers in heats
lasting 30-50 minutes \citep{booth1995}.  Points are awarded on a
10-point scale: each of five judges awards points to a surfer riding a
particular wave.  The World Surf League (WSL) is the main governing
body for professional surfers \citep{wsl}.  The WSL conducts a world
tour in which the best ranked 34 surfers compete; in addition, at each
tour venue, two ``wildcard" surfers also enter the competition, who
are ignored here due to their generally poor performance and low
participation.

@@

\noindent where $p_H$ is a quantification of the beneficial home
ground effect.  Similar techniques have been used to account for the
first-move advantage in chess~\citep{hankin2020}, and here we apply it
to assess the supposed Brazilian preference for particular wave types.
